Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-23 paper/paper.Rmd
more reorg

We begin by describing the general method of the class, then discuss shared methods for the replications and the process of development for each project.

## General Class Outline

All projects were completed as part of a graduate-level methodology class. At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project. The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.

All study participants were recruited on AMT. Individual sample sizes are given in Table \ref{tab:summary}. Each sample was recruited independently, using the same account but a different title.

Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT. For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study. In four cases, we powered the replication attempt to 80\% post-hoc power. In four cases, we used the original sample size. In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect. In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.

## Workflow

@@

All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis. A schematic of our class workflow is shown in Figure 1. Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.

@@

## Statistical approach

Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging for us to identify a single key statistical test for each study. Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution. Despite this interpretive difficulty, following previous work, we attempted to use a single statistical test as our target for replication planning and analysis.

@@

## Pedagogical Assessment

@@

## Pedagogical Implications

@@

@@

@@

## Decision Points for Instructors

- how to customize for different levels of instructor

### Study selection

- student expertise
- group wiork
- Strength of evidence in original, e.g. BF > 3

### Contacting original authors

### Results deposit

@@

## Confirmatory analyses

@@

## Implications for Replication Research

@@

>>>>

We begin by describing the details of our course projects. Below, in the subsection on Pedagogical Implications, we discuss broader decision points for the course design that other instructors might consider.

All projects were completed as part of a graduate-level methodology class. At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project. The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.  A schematic of our class timeline is shown in Figure 1.

@@

All study participants were recruited on AMT. Individual sample sizes are given in Table \ref{tab:summary}. Each sample was recruited independently, using the same account but a different title. Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT. For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.

We determined sample sizes using a case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget (see below for discussion).^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study. In four cases, we powered the replication attempt to 80\% post-hoc power. In four cases, we used the original sample size. In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect. In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.

@@

## Statistical Approach

Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging for us to identify a single key statistical test for each study. Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution (see Empirical Results and Discussion below). Despite this interpretive difficulty, following previous work, we attempted to use a single statistical test as our target for replication planning and analysis.

@@

## Results: Pedagogical Assessment

@@

## Discussion: Pedagogical Implications

@@

HOW CAN THIS BE GENERALIZED

### Models for students of different levels

@@

+ every student a separate project
+ group projects
+ single class projects

### Project selection

Greater/lesser proejct curation

### Subject population

We

Contacting original authors

### Workflow selection

@@

All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser. All analyses were written using R, a free and open-source platform for statistical analysis.  Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.

@@

## Results

All reported results are from pre-registered, confirmatory analyses.

@@

## Discussion: Implications for Replication Research

@@

<!-- MORE INSPIRATIONAL MATERIAL  -->
